Linear analysis of the vertical shear instability in astrophysical disks

### 2015-02-07 linear_iso.tex
major updating
updating

\section{Analytical discussion of vertically isothermal
  disks in the framework of the vertically global shearing
  box}\label{analytical}  
We begin with a discussion of vertically isothermal disks
where $\Gamma=1$, then $c_s$ is a constant. We  
first examine isothermal perturbations ($\gamma\equiv1$ and any value
of $\beta$, or any value of $\gamma$ with $\beta = 0$) before
considering the effect of finite thermal relaxation. 
In order to facilitate an analytical discussion, we introduce a number
of approximations below that allows a simple governing equation to be
derived and directly compared with previous works.

@@

\subsection{Isothermal perturbations}\label{iso_discuss}
Isothermal perturbations corresponds to $\gamma=1$ for any thermal
relaxation timescale $\beta$, or for any adiabatc index $\gamma$ when
$\beta=0$. In either case $\chi=1$ and Eq. \ref{ode_Q} implies 
\begin{align}
  Q = W, 
\end{align}
 and so 
 \begin{align}
   \ii\hat{\sigma}c_s\delta v_z = W^\prime
   % \quad   \text{(isothermal perturbations)},
 \end{align}
from Eq. \ref{lin_vz}. For isothermal perturbations 
the parameter $\chi=1$ so it is easiest to work with
$W$ by integrating Eq. \ref{vertiso_gov_nondim}. For later discussion
it is convenient to write the result as

@@

We remark that Eq. \ref{iso_ode1} is also applicable for  $\gamma=\Gamma\neq 1$ in the
limit $t_c\to\infty$ (i.e. neutrally stratified adiabatic disks),
since in that case $Q\simeq W$ as well. However, the following
discussion is only  valid for $\gamma=\Gamma=1$ because $c_s$ is taken
to be a constant.

>>>>

\section{Analytical discussion of vertically isothermal
  disks in the framework of the vertically global shearing
  box}\label{analytical}  
We begin with a discussion of vertically isothermal disks
where $\Gamma=1$, then $c_s$ is a constant. We  
first examine isothermal perturbations ($\beta = 0$) before
considering the effect of finite thermal relaxation. 
In order to facilitate an analytical discussion, we introduce a number
of approximations below that allows a simple governing equation to be
derived and directly compared with previous works.

@@

\subsection{Isothermal perturbations}\label{iso_discuss}
Isothermal perturbations correspond to $\beta\equiv0$, 
%relaxation timescale $\be
%or for any adiabatc index $\gamma$ when
%$\beta=0$. 
so $\chi=1$ and Eq. \ref{ode_Q} implies 
\begin{align}
  Q = W, 
\end{align}
 and so 
 \begin{align}
   \ii\hat{\sigma}c_s\delta v_z = W^\prime
   % \quad   \text{(isothermal perturbations)},
 \end{align}
from Eq. \ref{lin_vz}. For isothermal perturbations 
the parameter $\chi=1$ so it is easiest to work with
$W$ by integrating Eq. \ref{vertiso_gov_nondim}. For later discussion
it is convenient to write the result as

@@

%We remark that Eq. \ref{iso_ode1} is also applicable for  $\gamma=\Gamma\neq 1$ in the
%limit $t_c\to\infty$ (i.e. neutrally stratified adiabatic disks),
%since in that case $Q\simeq W$ as well. However, the following
%discussion is only  valid for $\gamma=\Gamma=1$ because $c_s$ is taken
%to be a constant.
